\beginrecipie{Caramel Drip Cake}{15}{45}{5}
\begin{ingredient}
    \begin{main}
        \item \cups{2} cups flour
        \item \cups{2} granulated sugar
        \item \teaspoons{1 1/2} baking powder
        \item \teaspoons{1/2} salt
        \item \cups{2/3} unsalted butter
        \item \teaspoons{1} vanilla extract
        \item \cups{2/3} egg whites
        \item \cups{1} buttermilk
    \end{main}
    \begin{subingredient}{caramel sauce}
        \item \cups{1} granulated sugar
        \item \tablespoons{6} unsalted butter
        \item \cups{1/3} heavy cream
        \item \teaspoons{1/4} salt
    \end{subingredient}
    \begin{subingredient}{caramel buttercream}
        \item \cups{2} unsalted butter
        \item \cups{7} powdered sugar
        \item \teaspoons{1} salt
        \item \tablespoons{1} heavy cream
        \item \teaspoons{1} vanilla extract
        \item \cups{1/3} caramel sauce
    \end{subingredient}
\end{ingredient}
\begin{recipe}
    \step{Preheat oven to 180°C. Line three 6-inch pans with parchment rounds, and grease with non-stick baking spray.}
    \step{Mix together all dry ingredients (flour, baking powder, sugar, and salt) until fully combined. Mix chunks of room-temperature butter slowly into the dry mix. Continue to mix until no large chunks of butter remain, and the mixture becomes crumbly.}
    \step{Slowly fold in the eggs and buttermilk. Mix in vanilla extract and oil.}
    \step{Divide batter evenly between the prepared cake pans. Bake for 30 minutes, or until a toothpick comes out clean. Allow the pans to cool for 10 minutes.}
    \step{Next, make the caramel sauce. Turn stove to medium heat, and place a pot over the element.}
    \step{Pour in sugar gradually, adding 1/4 cup at a time, waiting until the sugar is mostly liquified.}
    \step{Turn off the heat and mix in butter slowly (1 Tbsp at a time), then stir in cream and salt. The mixture will be very thin. Cool in the fridge for 20 minutes to solidify.}
    \step{To make the caramel buttercream, beat the butter and mix in vanilla and salt on a low speed.}
    \step{Slowly add in the powdered sugar, 1 cup at a time. Alternate with the heavy cream and caramel, which will help thin the frosting.}
    \step{Stack and frost cake layers on a greaseproof cake board. Add an even layer of salted caramel buttercream between each cake layer, as well as a large swirl of caramel sauce.}
    \step{Spread a thin coat of frosting around the the cake to fully cover the cake layers. Chill the cake in the fridge until the frosting is firm. Add a second, thicker layer of frosting to the cake, and smooth.}
    \step{Chill the cake for an additional 10 minutes, use the caramel sauce to add drips around the cake. Cover the top of the cake with caramel sauce, and add caramel squares around the top of the cake.}
\end{recipe}